A comparative risk assesment of U.S. regional active transport using the ITHIM model

### 2016-09-21 R/ITHIM.Rmd
Expanded grid for Regional Analysis
Tweaked the figures and removed AgeClass1 from DALY count and figure 1

```{r loadITHIM, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = FALSE}
library("devtools")
install_github("smbache/magrittr", ref="master")
library("magrittr")
install("~/ITHIM/")
library("ITHIM")
```

@@

#RwtList <- lapply( , function(x) ifelse(x == 0, 0, x) )
#RctList <- lapply( , function(x) ifelse(x == 0, 0, x) )

@@

```{r foobar, eval = TRUE, echo = FALSE}
sumDALY <- function(ITHIM.baseline, ITHIM.scenario){
    return(sum(unlist(compareModels(ITHIM.baseline, ITHIM.scenario)$daly.delta)))
    }
```

```{r ITHIMObjs, eval = TRUE, fig.width = 8, fig.height = 5, echo = FALSE, warning = FALSE}
upper <- 10
length <- 100

@@

  DALYs <- lapply(ITHIMList, sumDALY, ITHIM.baseline = ITHIM.national)
  DALYs <- data.frame(HHS = names(DALYs), muNonTravel = muNonTravel, DALY = unlist(DALYs))
  DALYsTotal <- rbind(DALYsTotal, DALYs)
}

barplot(with(NHTS,table(HHS)))

p <- ggplot(DALYsTotal, aes(x = muNonTravel, y = DALY/1e3, colour = HHS))

@@

```{r meanMatrices, eval = TRUE, fig.width = 10, fig.height = 5, warning = FALSE, message = FALSE, echo = FALSE}

ITHIMList <- c(ITHIMList, list("Natl" = ITHIM.national))

meanMatrix <- function(ITHIM, mode = "walk"){
   if(mode == "walk"){
      return(with(ITHIM$parameters, data.frame(ageClass = factor(1:8), mode = mode, Rwt*muwt)))
}else{
      return(with(ITHIM$parameters, data.frame(ageClass = factor(1:8), mode = mode, Rct*muct)))
}
}

meanMatrixListWalk <- lapply(ITHIMList, meanMatrix, mode = "walk")
meanMatrixListCycle <- lapply(ITHIMList, meanMatrix, mode = "cycle")

D <- melt(c(meanMatrixListWalk,meanMatrixListCycle))
names(D) <- c("ageClass", "mode", "sex", "time", "HHS")

p1 <- ggplot(D, aes(x = ageClass, y = time, fill = sex)) + geom_bar(stat= "identity", position = "dodge") 
p1 + theme_bw() + scale_x_discrete(name="Age Class", breaks = c(2,4,6,8)) + scale_y_continuous(name="Travel Minutes per Week") + facet_grid( mode ~ HHS, scales = "free_y")

>>>>

```{r loadITHIM, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = FALSE}
library("devtools")
install_github("smbache/magrittr", ref="master")
library("magrittr")
install("~/ITHIM/")
library("ITHIM")

fig.width <- 6 # inches
phi <- (1+sqrt(5))/2 # the golden ratio ;)
```

@@

@@

```{r foobar, eval = TRUE, echo = FALSE}
sumDALY <- function(ITHIM.baseline, ITHIM.scenario){
    return(sum(unlist(data.frame(compareModels(ITHIM.baseline,ITHIM.scenario)$daly.delta)[-1,]))) # AgeClass 1 is removed from totals
    }
```

```{r ITHIMObjs, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, echo = FALSE, warning = FALSE}
upper <- 20
length <- 100

@@

  DALYs <- lapply(ITHIMList, sumDALY, ITHIM.baseline = ITHIM.national)
  DALYs <- data.frame(Region = names(DALYs), muNonTravel = muNonTravel, DALY = unlist(DALYs))
  DALYsTotal <- rbind(DALYsTotal, DALYs)
}

barplot(with(NHTS,table(Region)))

p <- ggplot(DALYsTotal, aes(x = muNonTravel, y = DALY/1e3, colour = Region))

@@

```{r meanMatrices, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, warning = FALSE, message = FALSE, echo = FALSE}

ITHIMList <- c(ITHIMList, list("National" = ITHIM.national))

meanMatrix <- function(ITHIM, mode = "Walking"){
   if(mode == "Walking"){
      return(with(ITHIM$parameters, data.frame(ageClass = factor(1:8), mode = mode, Rwt*muwt)))
   }else if (mode == "Cycling"){
      return(with(ITHIM$parameters, data.frame(ageClass = factor(1:8), mode = mode, Rct*muct)))
   }else{
      message("error in meanMatrix function")
   }
}

meanMatrixListWalk <- lapply(ITHIMList, meanMatrix, mode = "Walking")
meanMatrixListCycle <- lapply(ITHIMList, meanMatrix, mode = "Cycling")

D <- melt(c(meanMatrixListWalk,meanMatrixListCycle))
names(D) <- c("ageClass", "mode", "Sex", "time", "Region")

D1 <- subset(D, Region %in% c("HHS01","HHS02","HHS09","HHS10","National") & ageClass != "1" )
D2 <- subset(D, !(Region %in% c("HHS01","HHS02","HHS09","HHS10")) & ageClass != "1" )

p1 <- ggplot(D1, aes(x = ageClass, y = time, fill = Sex)) + geom_bar(stat= "identity", position = "dodge") 
p1 + theme_bw() + scale_x_discrete(name="Age Class", breaks = c(2,4,6,8)) + scale_y_continuous(name="Travel Time per Week (minutes)") + facet_grid( mode ~ Region, scales = "free_y")

p2 <- ggplot(D2, aes(x = ageClass, y = time, fill = Sex)) + geom_bar(stat= "identity", position = "dodge") 
p2 + theme_bw() + scale_x_discrete(name="Age Class", breaks = c(2,4,6,8)) + scale_y_continuous(name="Travel Time per Week (minutes)") + facet_grid( mode ~ Region, scales = "free_y")

### 2016-09-21 manuscript/manuscript.tex
Tweaked the figures and removed AgeClass1 from DALY count and figure 1

\begin{figure}[t]
    \centerline{\includegraphics[width=0.4\textwidth]{./figures/fig3}}
    \caption{Foo}\label{meanMatrices}
\end{figure}

@@

\begin{figure}[t]
    \centerline{\includegraphics[width=0.4\textwidth]{./figures/HHSmap}}
    \centerline{\includegraphics[width=0.4\textwidth]{./figures/fig2}}
    \caption{Change in total national DALYs for each regional
      transportation estimates.}\label{dalyFigure}
\end{figure}

>>>>

\begin{figure}[t]
  \centerline{\includegraphics[width=0.5\textwidth]{./figures/fig3}}
    \caption{Mean travel time by mode (walking/cycling) for each of
      the four regions with a decrease in DALYs
      $(\textrm{HHS01},\textrm{HHS02},\textrm{HHS09},\textrm{HHS10})$. The
      national means are displayed on the far right.  These four
      regions correspond to New England/NewYork and the West
      Coast.}\label{meanMatrices}
\end{figure}

@@

\begin{figure}[t]
    \centerline{\includegraphics[width=0.5\textwidth]{./figures/fig1}}
    \centerline{\includegraphics[width=0.5\textwidth]{./figures/fig2}}
    \caption{Change in total national DALYs for each regional
      transportation estimates.}\label{dalyFigure}
\end{figure}
